### 2021-07-08 newvariant.tex
lots of edits

The integral of the kernel $\RR_x(t) = \int K_x(t, \tau) \dtau$ is referred to as the instantaneous reproduction number, which is defined as secondary infections that would be caused by an individual infected at time $t$ if conditions were to remain the same \citep{fraser2007estimating}.
The instantaneous reproduction number is a particular kind of weighted average of infectiousness of previously infected individuals at time $t$---in particular, it is weighted by the total relative infectiousness at time $t$, rather than by the actual number of infected individuals present.
The normalized kernel $g_x(t, \tau) = K_x(t, \tau)/\RR_x(t)$---which we refer to as the instantaneous generation-interval distribution---describes the relative contribution of previously infected individuals to current incidence $i_x(t)$ and provides information about the time scale of disease transmission.
Like the instantaneous reproduction number, the instantaneous generation-interval distribution describes when an individual infected at time $t$ will transmit infections if conditions were to remain the same.
Both the reproduction number and the generation-interval distribution depend on many factors, including intrinsic infectiousness of an infected individual, non-pharmaceutical interventions, awareness-driven behavior, and population-level susceptibility \citep{fraser2007estimating}.

@@

>>>>

The integral of the kernel is referred to as the instantaneous reproduction number:
\begin{equation}
\RR_x(t) = \int K_x(t, \tau) \dtau
\label{eq:instR}
\end{equation}
which is defined as secondary infections that would be caused by an individual infected at time $t$ if conditions were to remain the same \citep{fraser2007estimating}.
The instantaneous reproduction number is a particular kind of weighted average of infectiousness of previously infected individuals at time $t$---in particular, it is weighted by the total relative infectiousness at time $t$, rather than by the actual number of infected individuals present.
The normalized kernel $g_x(t, \tau) = K_x(t, \tau)/\RR_x(t)$---which we refer to as the instantaneous generation-interval distribution---describes the relative contribution of previously infected individuals to current incidence $i_x(t)$ and provides information about the time scale of disease transmission.
Like the instantaneous reproduction number, the instantaneous generation-interval distribution describes when an individual infected at time $t$ will transmit infections if conditions were to remain the same.
Both the reproduction number and the generation-interval distribution depend on many factors, including intrinsic infectiousness of an infected individual, non-pharmaceutical interventions, awareness-driven behavior, and population-level susceptibility \citep{fraser2007estimating}.

@@

\begin{figure}[!th]
\begin{center}
\includegraphics[width=0.95\textwidth]{control_sim.pdf}
\caption{
\textbf{Simulations of constant-strength and constant-speed interventions.}
Constant-strength (A--C) and constant-speed (D--F) interventions are simulated using the renewal equation (see Supplementary Materials for details of simulations).
(A,D) Daily incidence of infections caused by the wild type ($\iw(t)$, gray) and the variant ($\iv(t)$, colored).
(B,E) Instantaneous reproduction number of the variant $\Rv(t)$ calculated using \eref{instR}.
(C,F) Proportion of incidence of infections caused by the variant ($\iv(t)/(\iw(t)+\iv(t))$). 
Epidemic trajectories are calculated assuming $\rw=0\pday$, $\delta=0.1\pday$, $\rv=0.1\pday$, $\Gy{wt}=5\,\textrm{days}$, and $\kappa=1/5$ for pre-intervention conditions, and then introducing constant-strength and constant-speed interventions on day 30.
The pre-intervention ratio between the mean generation interval $\Gy{var}/\Gy{wt}$ is assumed to equal 1.5 (longer), 1 (equal), and 1/1.5 (shorter) for three different scenarios.
The constant-strength and constant-speed interventions are identically modeled as illustrated in \fref{strengthspeed}.
}
\end{center}
\label{fig:control_sim}
\end{figure}

Finally, we synthesize our findings and illustrate the differences between constant-strength and constant-speed interventions using epidemic simulations using the renewal equation (\fref{control_sim}).
